### 2019-03-10 paper/sex_selection_spacing-ver2.tex
Remove discussion of methods not shown in paper

Because the probability of ever having a next birth likely varies across groups, a direct 
comparison of standard survival curves tells us little about how the spread of sex selection 
affects birth spacing across groups.
I, therefore, condition on the predicted likelihood of parity progression when examining 
birth spacing measures, such as the median duration to a birth.
The reliability of this approach depends on whether the spell length covered is 
sufficiently long that few women are likely to give birth after the spell cut-off.
I discuss the choice of spell length below.%
\footnote{
It is important to note that the approach is not the same as merely calculating 
the birth spacing measures for women who already have a given 
parity child in the survey because that number does not take into account
the censoring of spells that will eventually lead to a birth.
}
In addition, I also present graphs of both standard survival curves and
survival curves conditional on parity progression (which therefore
begin at 100\% and end at 0\%).

Interpretation of the model coefficients is challenging \citep{thomas96}.
It is, however, possible to calculate the predicted probabilities of 
having a boy, $b$, and of having a girl, $g$, in period $t$, conditional on 
a set of explanatory variables and not having had a child before that period, as
\begin{align}
P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt}, t ) 
& =  
\frac{ \exp(D_j(t) + \alpha_{1t}' \mathbf{Z}_{kt} + \beta_1' \mathbf{X}_{k} )}
{1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt} ' \mathbf{Z}_{kt} + \beta_l ' \mathbf{X}_{k})}
\label{eq:probability_boy} \\
P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t ) 
& =  
\frac{ \exp(D_j(t) + \alpha_{2t}'\mathbf{Z}_{kt} + \beta_2'\mathbf{X}_{k} )}
{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{kt} + \beta_l'\mathbf{X}_{k})}
\label{eq:probability_girl}
\end{align}
It is then straightforward to calculate the estimated percentage of children born that 
are boys, $\hat{Y}$, at each $t$:  
\begin{equation}
\hat{Y}_t 
= 
\frac{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )}
{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
\times 100.
\label{eq:probability_son}
\end{equation}
Combining the percentage boys and the likelihood of exiting the spell 
across all $t$ gives the predicted percent boys born over the entire spell.
In addition to the predicted percent boys over the entire spell, 
I also present graphs of how the percentage boys born vary across time
within a spell, together with the associated confidence interval for given 
values of explanatory variables calculated using the Delta method.

>>>>

Because the probability of ever having a next birth varies across groups, a direct 
comparison of standard survival curves tells us little about how the spread of sex 
selection affects birth spacing across groups.
I, therefore, condition on the predicted likelihood of parity progression when examining 
birth spacing measures, such as the average duration to a birth.
The reliability of this approach depends on whether the spell length covered is 
sufficiently long that few women are likely to give birth after the spell cut-off.
I discuss the choice of spell length below.%
\footnote{
It is important to note that the approach is not the same as merely calculating 
the birth spacing measures for women who already have a given 
parity child in the survey because that number does not take into account
the censoring of spells that will eventually lead to a birth.
}
In addition, I present graphs of survival curves conditional on parity progression,
which therefore begin at 100\% and end at 0\%.

Interpretation of the model coefficients is challenging \citep{thomas96}.
It is, however, possible to calculate the predicted probabilities of 
having a boy, $b$, and of having a girl, $g$, in period $t$, conditional on 
a set of explanatory variables and not having had a child before that period, as
\begin{align}
P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt}, t ) 
& =  
\frac{ \exp(D_j(t) + \alpha_{1t}' \mathbf{Z}_{kt} + \beta_1' \mathbf{X}_{k} )}
{1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt} ' \mathbf{Z}_{kt} + \beta_l ' \mathbf{X}_{k})}
\label{eq:probability_boy} \\
P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t ) 
& =  
\frac{ \exp(D_j(t) + \alpha_{2t}'\mathbf{Z}_{kt} + \beta_2'\mathbf{X}_{k} )}
{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{kt} + \beta_l'\mathbf{X}_{k})}
\label{eq:probability_girl}
\end{align}
It is then straightforward to calculate the estimated percentage of children born that 
are boys, $\hat{Y}$, at each $t$:  
\begin{equation}
\hat{Y}_t 
= 
\frac{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )}
{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
\times 100.
\label{eq:probability_son}
\end{equation}
Combining the percentage boys and the likelihood of exiting the spell 
across all $t$ gives the predicted percent boys born over the entire spell.
